---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fixbatch

<!-- badges: start -->
<!-- badges: end -->

## Update

### fix bug 2020-12-17

- [x] add the function to select housekeep gene Separately from every batch group

- [ ] add the `cpm` function to calculate the adjuts expression cpm value form `egdeR`
- [ ] add the `combat` function form `sva`


the R packages is full fo bugs, beacuse it's a naive packagse, so I suggest every time when you use the R packages, should update R packages fristly. remember IT is everytime!

```{r echo=FALSE}
#devtools::update_packages("fixbatch")
```

## Insatll

```{r echo=FALSE}
#devtools::install_github("wangjiaxuan/fixbatch")
```

```{r setup}
library(fixbatch)
```

## Function

### col_cv 

calculate the coefficient of variation of the row value in a gene expression matrix.

### col_sum

calculate the sum the row value in a gene expression matrix.

### housekeep

According to the coefficient of variation and the expression sum, the stable observation value is selected

## batch_housekeep

he function to select housekeep gene Separately from every batch group

### norm_fix

norm_fix allows users to adjust for batch effects in datasets where the batch covariate is known, using the packages `preprocessCore`, and the function normalize.quantiles.

## website

[处理批次效应连续剧第一集(失败的R包)](https://abego.cn/2020/12/14/remove-the-batch-effect-series-1-a-imcomplete-r-package/)
>>>>>>> df358909355a58c9055eecbb5f4f704bb99acceb
